Last glacial cycle glacier erosion potential in the Alps

### 2021-01-29 articles/erosion/alps-erosion.tex
Add references I thought of in the intro.

%\usepackage{doi}
\usepackage{authblk}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[pdftex]{xcolor}
\usepackage[pdftex]{graphicx}
\usepackage[authoryear,round]{natbib}

@@

    The glacial erosion landscape of the Alps has fascinated generations of
    explorers, artists, mountaineers and scientists for centuries. Its cultural
    impact is indeed so far-reaching, that in English, a non-Alpine language,
    the adjective ``alpine'' with non-capital ``a'' is now casually used to
    describe an Alpine-like, glacially modified mountain landscape outside the
    Alps, while the proper noun ``Alps'' has been applied to nick-name
    Alpine-like, glacier eroded mountain ranges in Norway (\emph{Lyngsalpene}),
    New Zealand (Southern Alps), Japan (\emph{Nihon Arupusu}), and elsewhere.

    Some mountain ranges are predominantly characterised by cirque glaciation
    (e.g. Uinta Mountains), glacial valleys (e.g. Putorana Plateau), or
    large-scale overdeepenings (e.g. Patagonia). But other regions, including
    the Alps, present a higher variety glacial erosional landforms
    (Fig.~\ref{fig:landscape}), whose implications on glacial history is yet to
    be understood.

    In absence of other glacial landforms, the degree of glacial modification
    of a landscape has sometimes been used as a proxy for the duration of past
    glacier cover, as for instance in geomorphological mapping \aref. However,
    cold-based glaciers have been shown to preserve landforms as fragile as
    sand beaches \aref. Yet it remains unclear how sharp the erosional
    transition to cold-based ice is, and why some glaciated regions show
    glacially preserved landscapes and others, including the Alps, do not
    \aref.

@@

    \begin{figure*}
      \centerline{\includegraphics{alpero_landscape}}
      \caption{%
        Alpine glacial erosion landscape diversity.
        \textbf{(a)} Piedmont overdeepening of Lake Constance, ca.~10x50\,km.
        \textbf{(b)} Glacial trough of Lauterbrunnental, ca.~1x10\,km.
        \textbf{(c)} Mountain cirque of Chüebodengletscher, ca.~1x1\,km.}
      \label{fig:landscape}
    \end{figure*}

>>>>

\usepackage{doi}
\usepackage{authblk}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[pdftex]{xcolor}
\usepackage[pdftex]{graphicx}
\usepackage[authoryear,round]{natbib}
%\usepackage{CJK}  % texlive-langjapanese

@@

    The glacial erosion landscape of the Alps has fascinated generations of
    explorers, artists, mountaineers and scientists for centuries. Its cultural
    impact is indeed so far-reaching, that in English, a non-Alpine language,
    the adjective ``alpine'' with non-capital ``a'' is now casually used to
    describe an Alpine-like, glacially modified mountain landscape outside the
    Alps, while the proper noun ``Alps'' has been applied to nick-name
    Alpine-like, glacier eroded mountain ranges in Norway (\emph{Lyngsalpene}),
    New Zealand (Southern Alps), Japan
    (\emph{%\begin{CJK}{UTF8}{min}日本アルプス\end{CJK},
    Nihon Arupusu}), and elsewhere.

    Some mountain ranges are predominantly characterised by cirque glaciation
    (e.g. Uinta Mountains), glacial valleys (e.g. Putorana Plateau), or
    large-scale overdeepenings (e.g. Patagonia). But other regions, including
    the Alps, present a higher variety glacial erosional landforms
    (Fig.~\ref{fig:landscape}), whose implications on glacial history is yet to
    be understood.
    In absence of other glacial landforms, the degree of glacial modification
    of a landscape has sometimes been used as a proxy for the duration of past
    glacier cover, as for instance in geomorphological mapping
    \citep[e.g.][]{Margold.etal.2011, Fu.etal.2012}. Cold-based glaciers have
    been shown to preserve landforms as fragile as sand beaches
    \citep{Kleman.1994}. Yet it remains unclear how sharp the erosional
    transition to cold-based ice is, and why some glaciated regions show
    glacially preserved landscapes and others, including the Alps, do not
    \citep{Wirsig.etal.2016, Seguinot.etal.2018}.

@@

    \begin{figure*}
      \centerline{\includegraphics{alpero_landscape}}
      \caption{%
        Alpine glacial erosion landscape diversity.
        \textbf{(a)} Piedmont overdeepening of Lake Constance, ca.~10x50\,km.
        \textbf{(b)} Glacial trough of Lauterbrunnental, ca.~1x10\,km.
        \textbf{(c)} Mountain cirque of Ch\"uebodengletscher, ca.~1x1\,km.}
      \label{fig:landscape}
    \end{figure*}
